---
title: "HW 02 - Water and Sanitation - Answer Key"
author: "Jesus Salazar"
date: "`r Sys.Date()`"
output: github_document
---

## Load packages and data

```{r load-packages-data, message = FALSE}
library(tidyverse)
wat_san <- read_csv("data/water-and-sanitation.csv")
```

## Exercises

### Exercise 1 -.5

5118

### Exercise 2

Looks like water samples taken from the same location in different countries.

### Exercise 3

Looks like people have been pooping less outside over the years. The bars get thinner over time.

```{r no-sanitation-years}
ggplot(data = wat_san, 
       mapping = aes(x = sanitation_none,)) +
  geom_histogram()+ facet_wrap(~Year)
```

### Exercise 4 -.5

For the year 2000, Cambodia had the least water infrastucture and had the highest no sanitation service. Eritrea  and Niger had low water infrastucter and high no sanitation services. There seems to be a correlation. 

```{r bottom-5-2000, echo=FALSE, fig.height=4, fig.width=4}
wat_san %>% group_by(Year)%>% filter(Year==2000) %>% arrange(desc(sanitation_none))
```

### Exercise 5

I do not see a relationship, the points are dispirsed, with a few condenced close to the 0 marks.

```{r all-2000-plot}
wat_san %>% filter(Year== 2000) %>%
  ggplot(wat_san, mapping = aes(x= water_none, y= sanitation_none))+
  geom_point()
```

### Exercise 6

Most of the countries changed but Niger went from second unsanitary to first. 

```{r bottom-5-2020}
wat_san %>% filter(Year== 2020) %>% arrange(desc(sanitation_none))
```

### Exercise 7 -.5
 
As the years go by, both values go down drastically. Sanitatin none and water none are linked.

```{r progress-summary, echo = F}
wat_san %>% 
  filter(Year == 2000 & Entity != "World" | Year == 2020 & Entity != "World") %>% 
  # this line uses a combination of logical operators (== (equal to), & (and), != (is not equal to), | (or))
  # this combination filters for the two years provided, while excluding any data associated with the "World" Entity
  group_by(Year) %>% 
  # this line groups all the data by Year, so that any summary statistics specified below are computed for each group
  summarize(water_none_min = min(water_none, na.rm = T),
            water_none_mean = mean(water_none, na.rm = T),
            water_none_median = median(water_none, na.rm = T),
            water_none_stdev = sd(water_none, na.rm = T),
            water_none_iqr = IQR(water_none, na.rm = T),
            water_none_max = max(water_none, na.rm = T),
            
            sanitation_none_min = min(sanitation_none, na.rm = T),
            sanitation_none_mean = mean(sanitation_none, na.rm = T),
            sanitation_none_median = median(sanitation_none, na.rm = T),
            sanitation_none_stdev = sd(sanitation_none, na.rm = T),
            sanitation_none_iqr = IQR(sanitation_none, na.rm = T),
            sanitation_none_max = max(sanitation_none, na.rm = T)

            )
```

### Exercise 8

As time went on, country sanitation improved for most countries all but two. 

```{r country-global-changes, echo = F}
wat_san %>% 
  filter(Entity == "World" |Entity == "Cambodia" | Entity == "India" | Entity == "Eritrea" | Entity == "Niger" | Entity == "Ethiopia") %>% 
  ggplot(aes(x = Year, y = sanitation_none, color = Entity)) +
  geom_line()
```

