---
title: "HW 02 - Water and Sanitation - Answer Key"
author: "Jesus Salazar"
date: "`r Sys.Date()`"
output: github_document
---

## Load packages and data

```{r load-packages-data, message = FALSE}
library(tidyverse)
wat_san <- read_csv("data/water-and-sanitation.csv")
```

## Exercises

### Exercise 1

5118

### Exercise 2

Looks like water samples taken from the same location in different countries.

### Exercise 3

Looks like people have been pooping less outside over the years. The bars get thinner over time.

```{r no-sanitation-years}
ggplot(data = wat_san, 
       mapping = aes(x = sanitation_none,)) +
  geom_histogram()+ facet_grid(~Year)
```

### Exercise 4

Insert your answer here...

```{r bottom-5-2000}

```

### Exercise 5

Insert your answer here...

```{r all-2000-plot}

```

### Exercise 6

Insert your answer here...

```{r bottom-5-2020}

```

### Exercise 7

Insert your answer here...

```{r progress-summary}
  
```

### Exercise 8

Insert your answer here...

```{r country-global-changes}

```
