---
title: "Lab 02 - Plastic waste"
author: "Jesus Salazar"
date: "2/2/2023"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

They all have density average around 5 units.

```{r plastic-waste-continent}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.7)
```

### Exercise 2

```{r plastic-waste-density}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.2)
```

### Exercise 3

Color and fill are examples of an aesthetic while the alpha is a modification of aesthetics that take place after it's coded in.

### Exercise 4

Data visualization is much more clearer with violin plots.

```{r plastic-waste-violin}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()
```

### Exercise 5

The lower the capita the less pollutive the country.

```{r plastic-waste-mismanaged}
ggplot(data = plastic_waste, 
       mapping = aes(x =  mismanaged_plastic_waste_per_cap, 
                     y = plastic_waste_per_cap)) +
  geom_point()
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
ggplot(data = plastic_waste, 
       mapping = aes(x =  mismanaged_plastic_waste_per_cap, 
                     y = plastic_waste_per_cap, color = )) +
  geom_point()
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```
